\documentclass{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{lipsum}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{fontawesome}
\usepackage{paracol}
\usepackage{parskip}
\usepackage[colorlinks=true, urlcolor=cyan, hypertexnames=false]{hyperref}
%\usepackage{etoolbox}

\renewcommand{\familydefault}{\sfdefault}

\title{Resume - Akshay Trivedi}
\author{Akshay Trivedi}

\renewcommand{\maketitle}{
\begin{center}
    {\Huge\bfseries \theauthor} {\huge (he/him)} \\
    \vspace{0.5em}
    \faPhone\enspace{}(510) 386-9255 \quad
    \faEnvelope\enspace{}\href{mailto:aku24.7x3@gmail.com}{aku24.7x3@gmail.com} \quad
    \faMapPin\enspace{}Fremont, CA \\
    \faGithub\enspace{}\href{https://github.com/SnootierMoon}{@SnootierMoon} \quad
    \faLinkedin\enspace{}\href{https://www.linkedin.com/in/akshay-trivedi21}{@akshay-trivedi21}
\end{center}
}

\titleformat{\section}{\huge\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{\parskip}

\titleformat{\subsection}{\large}{}{0em}{}
\titlespacing{\subsection}{0pt}{5pt}{0pt}

\titleformat{\subsubsection}{\bfseries}{}{0em}{}

\newenvironment{experience}[4]
{
    \subsection{\textbf{#1}, #2\texorpdfstring{\hfill}{ }\normalsize #4}
    \ifstrempty{#3}{}{\textit{#3}}
    \begin{list}{}{
        \setlength{\labelwidth}{3em}
        \setlength{\labelsep}{0em}
        \setlength{\itemsep}{-3pt}
        \setlength{\leftmargin}{0.2in}
        \setlength{\rightmargin}{0in}
        \setlength{\itemindent}{0em}
    }
}
{
    \end{list}
}

\begin{document}
\maketitle

\columnratio{0.67}
\begin{paracol}{2}

\section{Professional Experience}

    \begin{experience}{Astera Labs}{Firmware Engineer}{San Jose, CA}{Jun 2025|Present}
    \item Developed firmware for PCIe Gen6 switches that play a significant role in Astera's rack-scale AI and compute platform. Worked at all three layers of PCIe - Transaction, Data Link, and Physical. Gained detailed knowledge of the PCIe 6.0 and PIPE 6.0 (PHY interface for PCIe) standards.
    \end{experience}

    \begin{experience}{Astera Labs}{Software Engineer Intern}{Santa Clara, CA}{May 2024|Aug 2024}
    \item Created a toolchain for configuring ASIC firmware, and developed infrastructure for testing pre-silicon ASIC firmware on an emulation platform. Used Jenkins, pytest, I2C.
    \item Gained some familiarity with the PCIe 6.0 standard.
    \end{experience}

    \begin{experience}{TabaPay}{Software Engineer Intern}{Mountain View, CA}{May 2023|Aug 2023}
    \item Designed and implemented an internal database for TabaPay employees to quickly view their clients' API configuration state. Used Golang and MySQL.
    \item Learned how the card acceptors industry works and gained valuable experience working in a fast-paced and dynamic startup environment.
    \end{experience}

\section{Education}

    \begin{experience}{University of Maryland}{B.S in CS and Math}{College Park, MD}{Aug 2022|May 2025}
    \item Networks (CMSC711, CMSC417), OS (CMSC412), Architecture (CMSC412), \linebreak Cryptography (CMSC456), Parallel Comp. (CMSC416), Algorithms (CMSC451), Data Struct. (CMSC420). Num. Analysis I (AMSC466), Lin. Alg. (MATH405), Combinatorics \& Graph Thy (MATH475), Axiomatic Set Thy (MATH446), Abstract Alg. (MATH403), Adv. Calc. I (MATH410), Prob. Thy (STAT410).
    \item GPA: 4.000.
    \end{experience}

\section{Projects}

    \begin{experience}{\href{https://snootiermoon.github.io/final_project_711.pdf}{Mixed Messages}}{Research Term Project}{CMSC711 Computer Networks @ UMD}{2025}
        \item Collaborated with two undergraduate classmates on a research paper on metadata-private distributed communication protocols.
    \end{experience}

    %\begin{experience}{Math Lore Project}{Term Research Project}{}{}
    %    \item 
    %\end{experience}

    \begin{experience}{Stannox}{Individual Hobby Project}{}{2021|Present}
        \item A cross-platform \href{https://en.wikipedia.org/wiki/Voxel}{voxel} art editing and rendering application with a client/server architecture designed for collaborative creation. Through its many iterations, this project taught me Zig, Rust, Vulkan, OpenGL, and WebGPU.
    \end{experience}

\switchcolumn
\section{About Me}

I am a systems programmer. I believe that planning, testing, and benchmarking are critical steps in making software. I design solutions that use available hardware resources efficiently.

I am drawn to systems programming because I enjoy tackling problems under constraints. In high school I used Desmos, an online graphing calculator with limited computing features, to build a UI for the game Connect 4, including the ability to play with intelligent computer opponents. This project exemplifies the nature of challenges that I aspire to solve in the future.

I am a fast learner; I'm good at understanding documentation and detailed requirements to determine the best solution to a problem.

I also know that I cannot solve the hardest problems on my own, and I often need to work with others to get things done. I am a team player, and I am good at asking for and giving help in a positive manner.

\section{Skills}

\textbf{Programming Languages}: Zig, Python, Rust, C/C++, Golang, Java.

Systems programming (firmware and software).

Graphics programming: OpenGL, Vulkan, and WebGPU.

PCIe 6.0 and PIPE 6.0 standards.

\section{Awards}

Dean's List; Fall 2022 to Spring 2025 - University of Maryland

\href{https://www.cs.umd.edu/article/2025/06/four-umd-undergraduates-honored-inaugural-grant-family-award}{Grant Family Outstanding Achievement Undergraduate Student Award in Computer Science and Mathematics}; May 2025 - University of Maryland

\end{paracol}
\end{document}
